Ceph Parallel File System Evaluation Report

### 2013-08-29 abstract.tex
minor fixing on abstract

Ceph is an open-source and emerging parallel distributed file and storage
system technology. It is designed to provide file system-level and object-level
access to data. By design, Ceph assumes running on unreliable and commodity
storage and network hardware and provides reliability and fault-tolerance
through pre-calculated and controlled object placement and data replication.

>>>>

Ceph is an open-source and emerging parallel distributed file and storage
system technology. By design, Ceph assumes running on unreliable and commodity
storage and network hardware and provides reliability and fault-tolerance
through controlled object placement and data replication.
